Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex

The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns, while outer-product computes the product of all pairs of elements from the input matrices. Further explanation is available in Section 2.2 of Zhang et al. [1].

@@

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer-product computes the product of all pairs of elements from the input matrices.
More detailed explanation is available in Section 2.2 of ~\cite{zhang2021gamma}.
Figures ~\ref{fig:spgemm_small} and ~\ref{fig:spgemm_large} show SpGEMM results with Finch and TACO.
Note that inner-product is very inefficient unless sparse matrices are nearly dense because the cost of intersections that incurs a lot of redundant traversals. For the output-product, TACO only supports the dense output: TACO does not support outer product due to its lack of support for scatter into a 2D workspace. So, due to memory constraints, we are unable to run TACO's outer-product for large sparse matrices. On the other hand, Finch supports scatter into 2D workspace, 
So, for large sparse matrices, we only compared Gustavson's algorithms.
\changwan{mention TACO's gustavson's algorithm is hard-wired}
As shown in Figure~\ref{fig:spgemm_small}, for inner-product, Finch achieves comparable performance with TACO, and for outer-product, the 
As shown in Figure~\ref{fig:spgemm_large}, for large sparse matrices, Finch outperforms TACO with an average speedup of 1.05.

>>>>

The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns, while outer-product computes the product of all pairs of elements from the input matrices. Further explanation is available in Section 2.2 of  ~\cite{zhang2021gamma}.

@@
